### 2019-05-25 Literature_Review/pages/review_content.tex
Changes; - More content to the literature review

Further research into creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}. Each publication has provided a new way to visually represent a key fingerprint. This list is by no means exhaustive but is used to depict amount of research into this topic.

@@

Minimal research has also focused on textual fingerprint representations and their respective security. Work by A. Karole and N. Saxena\cite{karole2009improving} is the only relevant research looking into ways to improve the security of a textual representation. This research aim is to improve the secure device pairing process of comparing two numerical values. The devices used (Nokia 6030b - Mid range devices at the time of publication) and short SAS compared results in findings that only slightly applicable in a fingerprint comparison context.

Aside from this research there has been no other publications exploring the security textual representations. This clearly shows the presence of a sizeable research gap in the available literature.

{\small \textbf{TODO: } \textit{Need to double check this, I think there might have been some work into sentences}}

@@

>>>>

Further research into creation of unique visual hash schemes have been performed by C Ellison \textit{et al.} \cite{ellison2003public} (Flag), Yue-Hsun Lin \textit{et al.}\cite{lin2010spate} (T-Flag) and work by MM Olembo \textit{et al.}\cite{olembo2013developing}. Each publication has provided a new way to visually represent a key fingerprint. Alongside the accademic literature there are more informally presented methods of visual fingerprints such as Unicorns\footnote{https://unicornify.pictures/} and Robots\footnote{https://github.com/e1ven/Robohash} This list is by no means exhaustive but is used to depict amount of research and work invested into this topic.

@@

Minimal research has also focused on basic textual fingerprint representations and their respective security. Work by A. Karole and N. Saxena\cite{karole2009improving} looked into ways to improve the security of a textual representation. This research aim is to improve the secure device pairing process of comparing two numerical values. The devices used (Nokia 6030b - Mid range devices at the time of publication) and short SAS compared results in findings that only slightly applicable in a fingerprint comparison context.

A more specific subsection of textual fingerprints is the use of words and sentences to encode hash digests. Some of the first work in this area was produced by Patrick Juola and Philip Zimmermann 
\cite{juola1996whole} and their work in generating a word list where phonetic distinctiveness was prioritised. 
The inital sampling of words was taken from the Grady Ward's Moby Pronunciator that contains a huge list of word/pronunciation pairs. Each word is mapped to one byte where the unique aspect of the word list is the separation of ``even'' and ``odd'' words where even byte positions sample from the even list and odd from the odd list. The effectively creates two sub-word lists. The pairing of these word lists were determined through the use of a Genetic algorithm. The paper also includes a study on effective measures of linguistic distances of words and provided an in-depth discussion into these areas.

Overall the paper provides a foundation for formalising the creation of an effective wordlists. A limitation, however, is the lack of empirical data gathered on the effectiveness of the word list. This was evaluated later by the work of Dechand \textit{et al.}
\cite{dechand2016empirical} and shown to be an effective encoding scheme.

\textbf{TODO: } Add Loud and Clear: Human-Verifiable Authentication Based on Audio

Aside from this research there has been more informal implementations. The first being by Michael Rogers\footnote{https://github.com/akwizgran/basic-english}. Rogers' implementation is a program designed to map fingerprints to pseudo-random poems. This implementation was empirically evaluated in work by Dechand \textit{et al.} that was discussed in the previous section and in their paper was considered a sentence generator.

@@

\textbf{TODO: } Need to include a statement expressing the overall gaps in the literature

### 2019-05-25 Papers/Notes_TeX/pages/paper_notes.tex
Changes; - More content to the literature review

>>>>

\section{Loud and Clear: Human-Verifiable Authentication Based on Audio}

Paper is in the context of secure device pairing. The paper proposes the use of Loud-and-Clear which uses text to speech to vocalise a robust english like sentence derived from a public key

"Stajano and Anderson proposed a method
for establishing keys by means of a link created through physical contact [9]."

``A number of efforts have been made to involve a human user in the secondary channel in order to manually verify/compare
keys (or hashes thereof) including [24, 11, 12] and [21].''

CHECK: Manual authentication for wireless devices.

``system represents a cryptographic hash as a series of six short (up to four-
letter) words'' - N. Haller. Rfc1760: The s/key one-time password system, 1995.

System truncates the hash and encodes into 10-bit sections.

The system is based of MadLib sentences that are used mainly as amusment for children where gaps in text are filled with nouns

The effort placed into making an order for the wordlist is similar to that of PGPfone. They effectively want to make sure that one bit change, results in a completely distinct word

The paper is not backed up by any empirical data and is just a technical description on the system. It included just a performance analysis.

\section{Whole-Word Phonetic Distances and the PGPfone Alphabet}

PGPfones designed solution was the development of a wordless based of military NATO codes.

The authors used Moby Pronunciator database of nearly 200,000 word/pronunciation pairs.

Use-case for these findings are when verification needs to occur over a auditory line.

Mentions on potential further work in the emprical evaluation of these points

TODO: An analysis of perceptual confusions among some English consonants
